Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-15 paper/tex/discussion.tex
finished editing Discussion

Sequels to this study will also address some shortcomings of our experimental procedure.
The fixed redshift grid shared between the codes may have unfairly penalized codes with a different native parameterization, as precision is lost when converting between formats.
Performance on sharply peaked \pzpdf s may have been suppressed across all codes due to the insufficient resolution of the redshift grid.
In light of the results of \citet[]{Malz:qp}, in future analyses we plan to switch from a fixed grid to the quantile parameterization or to permit each code to use its native storage format provided they all store the same number of parameters.

@@

The goals of future investigations will require a realistically complex data set of higher sophistication than the DC1 data set used here.
%\item \red{inclusion of photometric errors, image based effects, blending, lensing, sky, mask, etc...}

The underlying dataset limited this work to a maximum redshift of $z=2$.
LSST imaging after 10 years of observations will include a significant number of $z>2$ galaxies in expected cosmology samples, and their inclusion does have potential significant implications for photo-$z$ measures: the high redshift galaxies lie at fainter apparent magnitudes and can have anomalous colours due to evolution of stellar populations and the shift to rest-frame magnitudes probing UV features of the underlying SED.
More importantly, one of the most common ``catastrophic outlier'' degeneracies observed in deep photometric samples occurs when the Lyman break is mistaken for the Balmer break, leading to multiple redshift solutions at $z\sim0.2-0.3$ and $z\sim2-3$ \citep{Massarotti:2001}.
This degeneracy, along with other potential degeneracies, are currently not covered by the limited redshift range of this initial paper, which could mean that we are not probing the full range of potential extreme outlier populations and how our \pz\ estimators respond to them.
Extending simulations to include the high-redshift galaxy population will be a priority in future data challenges.

This initial paper explored a data set that was constructed at the catalog level, with no inclusion of the complications that come from measuring photometry from images.
Future data challenges will move to catalogs constructed from mock images, including effects that will have great impact on \pz\ estimates, which will naturally include the complications of object blending, sensor effects, different observing conditions, amongst others.
Object blending will be a major area of investigation, as the mixing of flux from multiple objects and the resultant change in measured colours is predicted to affect a large fraction of LSST galaxies \citep{Dawson:2016}, and will be one of the major contributing systematics for photo-$z$'s.

The DC1 galaxy SEDs were linear combinations of just five basis SED templates, but a next generation of data for \pzpdf\ investigations must include a broader range of physical properties.
A subsequent study must also have a data set that includes active galactic nuclei (AGN) features in the SEDs, which perturb colours and other host galaxy properties.

In this study we have not accounted for the presence of Active Galactic Nuclei (AGN) contributions to galaxy fluxes.
In some cases, AGN will be easily identified from the colors and morphologies, i.e. the case of the brightest quasars where the nuclear activity outshines the host galaxy, and numerous studies have utilized color selection to create large samples of quasars \citep[e.g.][]{Richards:06,Maddox:08,Richards:15}.
In current deep fields, similar in depth to what we expect from \lsst, variability information and multi-wavelength data have been critical to not only identify AGN dominated galaxies, but also obtain more accurate photometric redshifts \citep[e.g][]{Salvato:11}.

In addition to AGN dominated galaxies, those with lower levels of nuclear activity present a more insidious problem, where AGN features may not be apparent, but the colours and other host galaxy properties are perturbed relative to galaxies with an inactive nucleus.
In such cases, the presence of the AGN may induce a bias if the template SEDs or empirical datasets do not include low-level AGN counterparts.
For LSST, we will need to identify and obtain accurate photometric redshifts of all types of AGN for a range of science goals, whether it is to eliminate such objects from cosmology experiments, or to use them with confidence, all the way through to understanding galaxy evolution and the role that AGN may play in influencing galaxy properties over cosmic time.

A promising route to classifying and obtaining accurate photometric redshifts for the AGN population is by combining machine learning with template-fitting techniques, as has recently been demonstrated by \citet{Duncan:18} for radio-selected AGN.
This is because AGN are relatively easy to obtain spectroscopic redshifts for over all redshifts due to the strong emission lines that they exhibit, allowing very good training sets for machine learning algorithms to use.
Whereas for those galaxies where the AGN is sub-dominant the galaxy templates are still adequate for obtaining reasonable photometric redshifts.

In addition to these improvements, the \lsstdesc \Pz\ Working Group plans to look at all potential methods to combine the results from multiple \pzpdf\ codes to improve accuracy, similar to the work presented in \citet{Dahlen:13,Carrascokind:14,Duncan:18}.
Taking advantage of multiple algorithms that use observables in slightly different ways has shown promise, however we must be very conscious of whether a potential combination properly treats the covariance between the methods, given that they are estimating quantities based on the same underlying observables.
Several science cases wish to estimate physical quantities along with redshift, for example galaxy stellar mass and star formation rate.
Proper joint estimation of redshift and physical quantities requires an in depth understanding of galaxy evolution, and progress on accurate bivariate redshift probability distributions will go hand in had with progress on understanding galaxies themselves.
Parameterization and storage of a complex 2-dimensional probability surface for potentially billions of galaxies (or even subsets of hundreds of thousand of particular interest) pose a potential challenge.
These issues will be examined in another future paper.

Finally, while this paper and future papers discussed above focus on photometric redshift codes and estimating accurate \pzpdf s from training data, we plan a separate, but complementary, project to examine calibration of the resultant redshifts via spatial cross-correlations \citep{Newman:2008}, which will be explored in a separate series of future papers.
The overarching plan describing everything laid out in this section is described in more detail in the \lsstdesc\ Science Roadmap (see Footnote in Section~\ref{sec:intro}).
These plans will require significant effort, but they are necessary if we are to make optimal use of the LSST data for astrophysical and cosmological analyses.

>>>>

Sequels to this study will also address some shortcomings of our experimental procedure.
The fixed redshift grid shared between the codes may have unfairly penalized codes with a different native parameterization, as precision is lost when converting between formats.
Performance on sharply peaked \pzpdf s may have been suppressed across all codes due to the insufficient resolution of the redshift grid.
In light of the results of \citet[]{Malz:qp}, in future analyses we plan to switch from a fixed grid to the quantile parameterization or to permit each code to use its native storage format under a shared number of parameters.

@@

To make optimal use of the \lsst\ data for cosmological and other astrophysical analyses of the Science Roadmap, future investigations that build upon this one will require a more sophisticated set of galaxy photometry and redshifts.
%\item \red{inclusion of photometric errors, image based effects, blending, lensing, sky, mask, etc...}
This initial paper explored a data set that was constructed at the catalog level, with no inclusion of the complications that come from measuring photometry from images.
Future data challenges will move to catalogs constructed from mock images, including the complications of deblending, sensor inefficiencies, and heterogeneous observing conditions, all anticipated to affect the measured colours of \lsst's galaxy sample \citep{Dawson:2016}.

The DC1 galaxy SEDs were linear combinations of just five basis SED templates, but a next generation of data for \pzpdf\ investigations must include a broader range of physical properties.
Though we only considered $z < 2$ here, \lsst\ 10-year data will contain $z > 2$ galaxies, plagued by fainter apparent magnitudes and anomalous colours due to stellar evolution.
A subsequent study must also have a data set that includes low-level active galactic nuclei (AGN) features in the SEDs, which perturb colours and other host galaxy properties.
An observational degeneracy between the Lyman break of a $z \sim 2-3$ galaxy from the Balmer break of a $z \sim 0.2-0.3$ galaxy is a known source of catastrophic outliers \citep{Massarotti:2001} that was not effectively included in this study.
To gauge the sensitivity of \pzpdf\ estimators to catastrophic outliers, our data set must include realistic high-redshift galaxy populations.

% In this study we have not accounted for the presence of Active Galactic Nuclei (AGN) contributions to galaxy fluxes.
% In some cases, AGN will be easily identified from the colors and morphologies, i.e. the case of the brightest quasars where the nuclear activity outshines the host galaxy, and numerous studies have utilized color selection to create large samples of quasars \citep[e.g.][]{Richards:06,Maddox:08,Richards:15}.
% In current deep fields, similar in depth to what we expect from \lsst, variability information and multi-wavelength data have been critical to not only identify AGN dominated galaxies, but also obtain more accurate photometric redshifts \citep[e.g][]{Salvato:11}.
%
% In addition to AGN dominated galaxies, those with lower levels of nuclear activity present a more insidious problem, where AGN features may not be apparent, but the colours and other host galaxy properties are perturbed relative to galaxies with an inactive nucleus.
% In such cases, the presence of the AGN may induce a bias if the template SEDs or empirical datasets do not include low-level AGN counterparts.
% For LSST, we will need to identify and obtain accurate photometric redshifts of all types of AGN for a range of science goals, whether it is to eliminate such objects from cosmology experiments, or to use them with confidence, all the way through to understanding galaxy evolution and the role that AGN may play in influencing galaxy properties over cosmic time.

% A promising route to classifying and obtaining accurate photometric redshifts for the AGN population is by combining machine learning with template-fitting techniques, as has recently been demonstrated by \citet{Duncan:18} for radio-selected AGN.
% This is because AGN are relatively easy to obtain spectroscopic redshifts for over all redshifts due to the strong emission lines that they exhibit, allowing very good training sets for machine learning algorithms to use.
% Whereas for those galaxies where the AGN is sub-dominant the galaxy templates are still adequate for obtaining reasonable photometric redshifts.

% In addition to these improvements, the \lsstdesc \Pz\ Working Group plans to look at all potential methods to combine the results from multiple \pzpdf\ codes to improve accuracy, similar to the work presented in \citet{Dahlen:13,Carrascokind:14,Duncan:18}.
% Taking advantage of multiple algorithms that use observables in slightly different ways has shown promise, however we must be very conscious of whether a potential combination properly treats the covariance between the methods, given that they are estimating quantities based on the same underlying observables.
% Several science cases wish to estimate physical quantities along with redshift, for example galaxy stellar mass and star formation rate.
% Proper joint estimation of redshift and physical quantities requires an in depth understanding of galaxy evolution, and progress on accurate bivariate redshift probability distributions will go hand in had with progress on understanding galaxies themselves.
% Parameterization and storage of a complex 2-dimensional probability surface for potentially billions of galaxies (or even subsets of hundreds of thousand of particular interest) pose a potential challenge.
% These issues will be examined in another future paper.

% Finally, while this paper and future papers discussed above focus on photometric redshift codes and estimating accurate \pzpdf s from training data, we plan a separate, but complementary, project to examine calibration of the resultant redshifts via spatial cross-correlations \citep{Newman:2008}, which will be explored in a separate series of future papers.
The overarching plan describing everything laid out in this section is described in more detail in the \lsstdesc\ Science Roadmap (see Footnote in Section~\ref{sec:intro}).
